---
title: "Migrants and Religion"
author: "Agnee Ghosh"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load necessary libraries
library(readxl)
library(dplyr)
library(ggplot2)

# Load the data (replace the file path with the correct one)
data <- read_excel("/Users/agneeghosh/Documents/GitHub/Incoming-and-Outcoming-Migrant-Counts/Incoming and Outgoing Migrant Counts.xlsx", sheet = "FOTM2")

# Inspect the data to find relevant columns
head(data)

colnames(data)

# Rename columns for simplicity
colnames(data) <- c("Direction", "Year", "Country", "Religion", "Count", "Percent", "Region", "Level", "CountryCode")

# Now filter and select
filtered_data <- data %>%
  filter(Religion != "All") %>%
  select(Religion, Count)

# Convert Count to numeric (it might be in character format initially)
filtered_data$Count <- as.numeric(filtered_data$Count)

# Summarize the data by religion
religion_summary <- filtered_data %>%
  group_by(Religion) %>%
  summarise(Total_Count = sum(Count, na.rm = TRUE))

# Calculate percentage distribution
religion_summary <- religion_summary %>%
  mutate(Percentage = Total_Count / sum(Total_Count) * 100)

# Define a pastel color palette
pastel_colors <- c("#FBB4AE", "#B3CDE3", "#CCEBC5", "#DECBE4", "#FED9A6", "#FFFFCC", "#E5D8BD", "#FDDAEC")

# Visualize the data with a bar plot using pastel colors
ggplot(religion_summary, aes(x = Religion, y = Percentage, fill = Religion)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = pastel_colors) +  # Apply pastel colors
  labs(title = "Religious Group Distribution Among Migrants",
       x = "Religion",
       y = "Percentage") +
  theme_minimal()

ggplot(religion_summary, aes(x = "", y = Percentage, fill = Religion)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  scale_fill_manual(values = pastel_colors) +  # Apply pastel colors
  labs(title = "Religious Group Distribution Among Migrants") +
  theme_void()